---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ptrr

<!-- badges: start -->
<!-- badges: end -->

This is a package for personal utilities.

It contains:

- RMarkdown templates and output formats
  - document
  - invoice
  - xaringan presentation
- `ggplot2` themes
- `drat` utilities
- `precommit` recipes
- font import utilities
- number, date and scale formatting functions
- Rmd templates and related utilities for repo doc, xaringan slides, and Rmd webpage

## Installation

You can install the latest release of ptrr from [Github](https://github.com) with:

``` r
devtools::install_github("petrbouchal/ptrr", ref = github_release())
```

The current development version is at

``` r
devtools::install_github("petrbouchal/ptrr")
```

There are also binaries in the `petrbouchal/drat` repo; this can be installed with

```{r}
install.packages("ptrr", repos = "https://petrbouchal.github.io/drat")
```


## TODO

- rounding function https://twitter.com/hspter/status/314858331598626816
- Czech scales
- Czech units
